% LaTeX Curriculum Vitae Template
% Copyright (C) 2004-2008 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper, 10pt]{article}
\usepackage{org-preamble}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{color}
\definecolor{webgreen}{rgb}{0,.5,0}
\definecolor{webbrown}{rgb}{.6,0,0}
\definecolor{webpurple}{rgb}{0.7,0,0.7}
% \usepackage{lmodern}
% \usepackage[osf]{mathpazo}

\hypersetup{
  breaklinks = true,  
  colorlinks=true, 
  anchorcolor= webbrown, 
  citecolor= webbrown,
  filecolor= webbrown, 
  linkcolor= webbrown, 
  menucolor= webbrown,
  urlcolor= webbrown, 
  citebordercolor= 1 0 0, 
  menubordercolor=1 0 0, 
  urlbordercolor=1 0 0, 
  runbordercolor=1 0 0 }
\hypersetup{pdfauthor=Rony Rodriguez-Ramirez}

\geometry{textheight=9.25in, textwidth=7.25in}

% Customize section headings
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\scshape\large}
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}

\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titlespacing\section{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

% Don't indent paragraphs.
\setlength\parindent{0em}
\setlength\parskip{0.5em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}
    { \setlength{\itemsep}{5pt}
      \setlength{\parsep}{0pt}
      \setlength{\topsep}{0pt}
      \setlength{\leftmargin}{0em} } }{
  \end{list}}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Rony Rodriguez Ramirez}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{The World Bank}
\def\myaddress{DECPI}
\def\myemail{rrodriguezramirez@g.harvard.edu}
\def\myweb{rrmaximiliano.github.io}
\def\myphone{(202) 876-6568}
\def\mytwitter{@rrmaximiliano}
\def\mygithub{github.com/RRMaximiliano}


\usepackage{float}
\usepackage{adjustbox}
%%%------------------------------------------------------------------------  
%%% Set fonts 
%%%------------------------------------------------------------------------

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\usepackage{fontspec}
\usepackage{fontawesome}
% \setfontfamily{\FA}{[FontAwesome.otf]}
% \setromanfont[Mapping={tex-text}, 
% 	Numbers={OldStyle},
% 	Ligatures={Common}]{Minion Pro}
\setmainfont[
 BoldFont=texgyrepagella-bold.otf,
 ItalicFont=texgyrepagella-italic.otf,
 BoldItalicFont=texgyrepagella-bolditalic.otf]{texgyrepagella-regular.otf}
% \setsansfont[Mapping=tex-text,Colour=darkblue]{Yanone Kaffeesatz-Medium}
\setmonofont[Mapping=tex-text,Scale=0.85]{Essential PragmataPro-R_1.3.otf}

\newfontface\scheader[SmallCapsFont={texgyrepagella-regular.otf},SmallCapsFeatures={Letters=SmallCaps}]{texgyrepagella-regular.otf}

%%%------------------------------------------------------------------------  
%%% Footer and Headers
%%%------------------------------------------------------------------------

% Make the style for vc-git revision control headers and footers
\usepackage[datesep=/]{datetime2}
% \DTMsetstyle{iso}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

\fancypagestyle{empty}{%
  \fancyhf{}% Clear header/footer
  \fancyfoot[C]{\scshape \thepage}
  \fancyfoot[R]{{\normalsize \texttt{Updated with commit \href{https://github.com/RRMaximiliano/rrmrr-vita/tree/\commithash}{\commitcode}\ on \today}}}
}

%%%------------------------------------------------------------------------  
%%% Cut Words
%%%------------------------------------------------------------------------
\hyphenation{Cen-tro-a-me-ri-ca-na}
\hyphenation{Ni-ca-ra-gua}
\hyphenation{Sung-kyun-kwan}

%%%------------------------------------------------------------------------  
%%% Begin Document
%%%------------------------------------------------------------------------

\begin{document}
\thispagestyle{empty}

\begin{center}
  {\Large\bf RONY RODRIGO MAXIMILIANO RODRÍGUEZ--RAMÍREZ} \\
  6 Appian Way, Cambridge, MA 02138  \\
  %\texttt{\href{https://twitter.com/RRMaximiliano}{\mytwitter}}\, \faTwitter \, 
  \texttt{\href{https://rrmaximiliano.github.io}{\myweb}}\, \faLink \, \texttt{\href{https://github.com/RRMaximiliano}{\mygithub}}\, \faGithub \, \texttt{\href{mailto:\myemail}{\myemail}}\, \faEnvelope
\end{center}

%% -------------------------------------------------------------------------------------------------
%% SECTIONS
%% -------------------------------------------------------------------------------------------------

%% -------------------------------------------------------------------------------------------------
%% EDUCATION
%% -------------------------------------------------------------------------------------------------

\section*{Education}

\begin{itemize}
%% Graduate studies
\item Ph.D. Harvard University \hfill 2027 (expected) \\
{\small \textit{Education Policy \& Program Evaluation} (Field Course: Economics
of Education)}
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]
    \item {\small \textbf{Awards}: Harvard University Presidential Fellow }
  \end{enumerate}

%% Graduate studies
\item M.Sc. KDI School of Public Policy and Management, Republic of Korea \hfill 2018 \\
{\small \textit{Development Policy} (Summa Cum Laude)}
  
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]
    \item {\small \textbf{Thesis:} Does the Small Business Program Benefit Self-Employed Workers? Evidence from Nicaragua. \\ 
    \textbf{Awards:} Outstanding Thesis Award, Academic Excellence Award \\ 
    \textbf{Concentrations:} Sustainable Development \textit{\&} Global Governance and Political Economy }
  \end{enumerate}
%% Undergraduate  
\item B.Sc. Universidad Centroamericana, Nicaragua \hfill 2015 \\
{\small \textit{Applied Economics} (Summa Cum Laude, Best Student Overall Performance, Top 1\%)}
  
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]
    \item {\small \textbf{Concentrations:} Economic \textit{\&} Territorial Development}
  \end{enumerate}
\end{itemize}

% \section*{Current Employment}
% \begin{itemize}
% \item Development Research Group, The World Bank \hfill 2021--Present \\
% {\small \textit{Research Consultant} }
%   \begin{enumerate}[leftmargin=10pt, label={}, nosep]
%     \item {\small \textbf{Project:} A sequential and adaptive experiment to increase the uptake of long-acting reversible contraceptives.} \\ {\small \textbf{PI:} Berk Özler; \textbf{Co-PIs:} Susan Athey, Julian C. Jamison.} {\small AEA RCT registry: \href{https://www.socialscienceregistry.org/trials/3514}{AEARCTR-0003514}}
%     \item {\small \textbf{Project:} Tech-enabled tutoring for learning re-engagement and recovery for adolescents in Ukraine.} \\ {\small \textbf{PI:} Lelys Dinarte; \textbf{Co-PIs}: Renata Freita Lemos.} {\small AEA RCT registry: \href{https://www.socialscienceregistry.org/trials/9328}{AEARCTR-0009328}}
%   \end{enumerate}  
% \end{itemize}




%% -------------------------------------------------------------------------------------------------
%% RESEARCH WORK
%% -------------------------------------------------------------------------------------------------

\section*{Publications}

%% Books
\subsection*{Books}

\begin{enumerate}[leftmargin=10pt, label={}, itemindent=-10pt, nosep]
\item Vegas, Emiliana, \textbf{Rony Rodriguez-Ramirez}, and Álvaro Hofflinger, "From
Closure to Recovery: Tracing the Educational Impact of COVID-19 in Chile," in
Harry Patrinos and Nuno Crato, eds., \textit{Learning Post Corona: What It Will Take to
Finally Improve National Education Systems?}, Springer: Washington, D.C.
Forthcoming. 
\item Sánchez, Mario, Douglas Castro, and \textbf{Rony Rodriguez-Ramirez},
"\href{http://biblioteca.clacso.edu.ar/Nicaragua/casc-uca/20150313124733/Ciudadania-y-violencia.pdf}{Citizenship
and violence: Deciphering their multiple expressions in Nicaragua}," Managua:
Centro de Análisis Socio-Cultural, 2015. 
\end{enumerate}

%% Non econ journal articles
\subsection*{Journal Articles}

\begin{enumerate}[leftmargin=10pt, label={}, itemindent=-10pt, nosep]
\item Kim, Booyuel, \textbf{Rony Rodriguez-Ramirez}, and Hee-Seung Yang, ``\href{https://www.tandfonline.com/doi/full/10.1080/19439342.2023.2300138}{Does the small business
program benefit self-employed workers? Evidence from Nicaragua.},''
\textit{Journal of Development Effectiveness}, January 2024, 1--20. 
\item Osorio, Hloreley and \textbf{Rony Rodriguez-Ramirez},
``\href{https://revistas.ucr.ac.cr/index.php/anuario/article/view/45081/44860}{Criticism
and Crisis in Nicaragua: The tension between Democracy and Capitalism},'' \emph{Anuario de Estudios Centroamericanos}, May 2020, \textit{46},1--42.
\item Sánchez, Mario, Douglas Castro, \textbf{Rony Rodriguez-Ramirez}, and Jorge
Guerra, ``\href{https://amnis.revues.org/2813}{Social movements and collective
action in Nicaragua: between identity, autonomy and subordination},'' \emph{Amnis}, September 2016, 15.

\item Siero, Carol, Sebastián Hernández, and \textbf{Rony Rodriguez-Ramirez},
``\href{http://www.uca.edu.ni/2/images/Revista-Encuentro/Revistas/e102/art-5.pdf}{Has
the international cooperation been important for development and economic
growth? Panel Evidence on Nicaragua and Central America},''
\emph{Encuentro}, December 2015, (102), 52--74.
\end{enumerate}

\subsection*{Working Papers}

%% Working Papers
\begin{enumerate}[leftmargin=10pt, label={}, itemindent=-10pt, nosep]
\item ``In utero exposure to civil conflict: Nicaraguan war and its long-term
effects on socio-economic outcomes,'' with Booyuel Kim and Hee-Seung Yang.
\item ``Online Tutoring in Pandemic and Conflict-affected Ukraine,'' with Lelys
Dinarte-Diaz, James Gresham, Renata Lemos, and Harry Patrinos. 
\end{enumerate}

%% Work in Progress
\subsection*{Selected Work in Progress}

\begin{enumerate}[leftmargin=10pt, label={}, itemindent=-10pt, nosep]
\item ``The Role of Selective Public Universities in Shaping Long-Term
Outcome,'' with Jostin Kitmang. 
\item ``Shared decision-making: Does quality of care affect contraceptive
use?,'' with Berk Özler, Katy Bergstrom, and Luca Parisotto.
  \item ``Abortion Ban and Socioeconomic Outcomes: Evidence from Nicaragua.''
\end{enumerate}

%% Reports
\subsection*{Reports}

\begin{itemize}
\item The World Bank,
``\href{https://documents1.worldbank.org/curated/en/099025312242111019/pdf/P1699940bcc13001a083820804f74e8151b.pdf}{Improving
the well-being of adolescent girls in developing countries},'' Author:
Washington, D.C., 2022. 
\end{itemize}

%% -------------------------------------------------------------------------------------------------
%% PROFESSIONAL EXPERIENCE: RESEARCH PLUS TEACHING
%% -------------------------------------------------------------------------------------------------

\section*{Professional Experience}

\subsection*{Current Research Assistanship}

\begin{itemize}
  \item Research Assistant to Professor Eric Taylor, Harvard University 
  \hfill 2024--Present 
  \item Research Assistant to Professor Dan Levy, Harvard University
  \hfill 2024--Present
  \item Research Assistant to Professor Emiliana Vegas, Harvard University
  \hfill 2023--Present
  \item Research Assistant to Dr. Álvaro Hofflinger, DRCLAS Harvard University
  \& Arizona State University
  \hfill 2023--Present
\end{itemize}

\subsection*{Research Experience}

\begin{itemize}
  \item Research Consultant--Development Research Group, Poverty and Inequality, The World Bank \hfill 2021--Present 
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]
    \item {\small \textbf{Project}: A sequential and adaptive experiment to increase the uptake of long-acting reversible contraceptives. \newline 
    \textbf{Country}: Cameroon} 
    \item {\small \textbf{Project}: Tech-enabled tutoring for learning re-engagement and recovery for adolescents in Ukraine. \newline 
    \textbf{Country}: Ukraine}
    \item {\small \textbf{Project}: Mental health and psychosocial support in Armenian schools. \newline 
    \textbf{Country}: Armenia}    
  \end{enumerate}
  \item Research Consultant--Development Impact Evaluation (DIME), The World Bank \hfill 2020--2021 
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]  
    \item {\small \textbf{Project}: Resolving land frictions to increase irrigation use and on-farm productivity. \newline \textbf{Country}: Rwanda.}
  \end{enumerate}
  \item Research Assistant to Professor Mauricio Romero. ITAM -- IPA. \hfill 2019--2020  
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]  
    \item {\small \textbf{Project}: The impact of outsourcing schools in Liberia. \newline \textbf{Country}: Liberia.}
  \end{enumerate}
  \item Research Assistant to Professor Nathaniel Lane, University of Oxford \hfill 2019--2020  
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]  
    \item {\small \textbf{Project}: The value of names - civil society, information, and governing multinationals on the global periphery. \\ \textbf{Country}: Cross-countries.}
  \end{enumerate}
  \item Research Assistant to Professor Hee-Seung Yang, KDI School of Public Policy and Management \hfill 2018--2019  
  \begin{enumerate}[leftmargin=10pt, label={}, nosep]  
    \item {\small \textbf{Project}: The long-term effects of the civil war in Nicaragua. \newline \textbf{Country}: Nicaragua.}
  \end{enumerate}
\end{itemize}

\subsection*{Teaching Experience}
\begin{itemize}
  \item Harvard University
  \hfill 2024--Present \\
{\small \emph{Teaching Feloow}.
\texttt{\href{https://github.com/harvard-api209/summer-assignments}{API-201 Math
Camp (Summer).}}}
  \item The World Bank \hfill 2021--2023 \\  {\small \emph{Instructor}.} \texttt{\href{https://github.com/worldbank/dime-r-training}{R for Stata Users}, \href{https://github.com/dime-worldbank/rrf-course}{\texttt{Reproducible Research Fundamentals}}}

  \item Lambda Institute, Perú \hfill 2020--2022 \\ {\small \emph{Instructor}.} \texttt{\href{https://github.com/lambda-stata/course-materials}{Advanced Stata for Economists}}; \href{https://github.com/lambda-stata/econometria-avanzada}{\texttt{Advanced Methods in Econometrics: Impact Evaluation}}
 
  \item Universidad Centroamericana, Nicaragua \hfill 2018 \\ {\small \emph{Adjunct Lecturer}.} \texttt{\href{https://github.com/econsoc-uca}{Social and Human Economy}}. \texttt{\href{https://rrmaximiliano.github.io/docs/evaluation-esh.pdf}{Evaluation: 4.9/5}}
  
  \item KDI School of Public Policy and Management, Republic of Korea \hfill
  2017--2018 \\ {\small \emph{Teaching Assistant}.}
  \texttt{\href{https://www.dropbox.com/home/teaching_materials/kdischool/spring_2018_impact_evaluation}{Impact
  Evaluation Methods}}; \texttt{\textcolor{webbrown}{Foundations of Sustainable
  Development}}
\end{itemize}

% \subsection*{Courses and Certifications}
% \begin{itemize}
%   \item Universidad de los Andes, Colombia \hfill 2021 \\
%   {\small \textit{Real Analysis}}
%   \item The World Bank, Washington DC \hfill 2022 \\
%   {\small \textit{Manage Successful Impact Evaluation Surveys}}
% \end{itemize}

%% -------------------------------------------------------------------------------------------------
%% HONORS and AWARDS
%% -------------------------------------------------------------------------------------------------

\section*{Seminars \textit{\&} Conference Presentations}

\begin{itemize}
  \item 2023. Stata Conference. 
  \item 2021. The World Bank DIME--KDI School joint conference on
  Impact Evaluation in Sustainable and Inclusive Development. 
  \item 2019. Allied Social Science Association (ASSA) meetings;
  Universidad Centroamericana. 
  \item 2018. 3ie International Initiative for Impact Evaluation--KDI
  School joint conference on Impact Evaluation; KAEA-KEA joint International
  Conference, Sungkyunkwan University; Korea and The World Economy, Jeju
  National; Asian Meeting of the Econometric Society, Sogang University. 
  \item 2017. 20th Anniversary of KDI School (poster session); The
  Ronald Coase Workshop, Xiamen University. 
  \item 2016. Central American Congress of Sociology. 
  \item 2015. VI Ethics Conference, Universidad Centroamericana; Interdisciplinary Research Congress, Universidad Centroamericana. 2014. Central American Congress of Sociology; Interdisciplinary Research Congress.
\end{itemize}

%% -------------------------------------------------------------------------------------------------
%% HONORS and AWARDS
%% -------------------------------------------------------------------------------------------------

\section*{Honors \textit{\&} Awards}
\begin{itemize}
\item Harvard University \hfill 2023 \\ {\small Presidential Scholar}
\item KDI School of Public Policy and Management. \hfill 2016--2018 \\ {\small Dean's list with distinction; Academic Excellence Award; Outstanding Thesis Award; Student Community Service Award.}
\item Korean Government Scholarship Program (KGSP), Government of Korea \hfill 2015-2018 \\ {\small Scholarship to pursue Master's studies. First Nicaraguan to be granted the scholarship.}
\item Universidad Centroamericana. \hfill 2015 \\ {\small  Best Student Performance Award. Awarded by the Applied Economics Department for the highest GPA.}
\item Universidad Centroamericana \hfill 2014 \\ {\small Young Researchers $1^{\textrm{st}}$ place. Research: ``Gender wage gap in Nicaragua'' with Sebastián Hernández.}
\item Universidad Centroamericana \hfill 2013 \\ {\small Young Researchers $3^{\textrm{rd}}$ place. Research: ``Determinants of access to credit in the urban sector'' with Sebastián Hernández. }
\end{itemize}


%% -------------------------------------------------------------------------------------------------
%% SOFTWARES RESOURCES
%% -------------------------------------------------------------------------------------------------
\section*{Software Development}

\begin{itemize}
  \item \textbf{Replication Packages}.
  \begin{enumerate}[leftmargin=10pt, label={}, itemindent=-10pt, nosep]
    \item with Mauricio Romero and Justin Sandefur. ``Beyond Short-term Learning Gains: The Impact of Outsourcing Schools in Liberia after Three Years.'' Published at the \textit{Economic Journal}. DOI:\href{https://doi.org/10.5281/zenodo.5579799}{10.5281/zenodo.5579799}
  \end{enumerate}
  \item \textbf{R Packages}. \newline \texttt{\href{https://github.com/RRMaximiliano/eleccionesNic}{eleccionesNic}}. Tidy datasets related to the elections in Nicaragua from 1990 to 2020. \newline \texttt{\href{https://github.com/RRMaximiliano/constitucionesNic}{constitucionesNic}}. Tidy datasets related to the political constitutions of Nicaragua for text mining. \newline \texttt{\href{https://rrmaximiliano.shinyapps.io/covid-nicaragua/}{COVID-19 en Nicaragua}}. Shiny app with tidy datasets of the COVID-19 pandemic in Nicaragua.
  \item \textbf{Stata Packages}. \newline
  \texttt{\href{https://github.com/RRMaximiliano/welfarefactor}{welfarefactor}}.
  A new distribution sensitive index for measuring welfare, poverty, and
  inequality.
  \newline \texttt{\href{https://github.com/worldbank/stata-linter}
  {stata\_linter}}. Opinionated detector that attempts to improve readability of Stata do files. \newline \texttt{\href{https://github.com/RRMaximiliano/send\_est}{send\_est}}. Sends estimates to \LaTeX. \newline \texttt{\href{https://github.com/RRMaximiliano/tvsc}{tvsc}}. Generates balance tables.
   \item \textbf{Selected GitHub Repositories and Data Initiatives}
   \newline U.S. Customs and Border Protection (CBP) Data of Nicaraguan Migrants \href{https://github.com/RRMaximiliano/migrants_usbp}{\faGithub}
   \begin{enumerate}[label = {-}]
    \item Information of all Nicaraguans that have been detained at the U.S. borders.
   \end{enumerate}
   National Police of Nicaragua Data repository \href{https://github.com/RRMaximiliano/policia-nacional-nic-stats}{\faGithub}
   \begin{enumerate}[label = {-}]
    \item The extracted data contains information for type of crime, complaints, and solved cases in Nicaragua from 1980 to 2019. First tidy dataset that is available to the public on crime in Nicaragua at the department level. 
   \end{enumerate}
   Coronavirus Data repository for Nicaragua \href{https://github.com/RRMaximiliano/observatorio-covid-nicaragua}{\faGithub}
   \begin{enumerate}[label = {-}]
    \item Non-official information on the state of COVID-19 in Nicaragua that allows users to use the datasets and plot information at the national and department level. 
   \end{enumerate}
   Nicaragua Rulers \href{https://github.com/RRMaximiliano/observatorio-covid-nicaragua}{\faGithub}
   \begin{enumerate}[label = {-}]
    \item Information on all the rulers of Nicaragua. Currently, the data in this repository contains information from the year 1,508 to 2,020. First tidy dataset that is available to the public on Nicaraguan rulers.
   \end{enumerate}
   Nicaraguan Population 18th and 19th Centuries \href{https://github.com/RRMaximiliano/poblacion-nicaragua-siglo-18-19}{\faGithub}
   \begin{enumerate}[label = {-}]
    \item Hand-coded information form archives on the Nicaraguan population in the 18th and 19th Centuries.
   \end{enumerate}
  %  Best Practices for Data and Code Management \href{https://github.com/RRMaximiliano/practicas-datos-codigos}{\faGithub}
  %  \begin{enumerate}[label = {-}]
  %   \item Translated to Spanish the document ``Best Practices for Data and Code Management'' by Innovations for Poverty Action (IPA).
  %  \end{enumerate}
\end{itemize}

%% -------------------------------------------------------------------------------------------------
%% LANGUAGE ANS SOFTWARE RESOURCES
%% -------------------------------------------------------------------------------------------------

\section*{Skills}
\begin{itemize}
\item \textbf{Software.} \newline Advanced: Stata, R, \LaTeX, Git(Hub), ODK
(SurveyCTO, KoboToolbox) \\
Intermediate: Python \\
Beginner: SQL, ArcGis, C, Java
\item \textbf{Language.} \newline Spanish (native) \\ English (fluent) \\ French
(C1) \\ Korean (TOPIK 4) \\ Nicaraguan Sign Language (LSN, Intermediate) \\ Latin
(Beginner)
\end{itemize}
\bigskip


% \section*{References}
% \begin{itemize}
%   \item Berk Özler, Ph.D. \hfill Mauricio Romero, Ph.D. \\
%   Lead Economist and Research Manager \hfill Assistant Professor \\
%   Development Research Group, The World Bank \hfill Instituto Tecnológico Autónomo de México \\
%   \texttt{\href{mailto:bozler@worldbank.org}{bozler@worldbank.org}} \hfill \texttt{\href{mailto:mtromero@itam.mx}{mtromero@itam.mx}}
%   \item Booyuel Kim, Ph.D. \hfill Hee-Seung Yang, Ph.D. \\
%   Associate Professor \hfill Associate Professor \\
%   Seoul National University \hfill Yonsei University \\
%   \texttt{\href{mailto:booyuel@snu.ac.kr}{booyuel@snu.ac.kr}} \hfill \texttt{\href{mailto:heeseung.yang@yonsei.ac.kr}{heeseung.yang@yonsei.ac.kr}}
% \end{itemize}

\end{document}